A Meta-Analysis of Music Emotion Recognition Studies

### 2025-03-10 manuscript/manuscript.qmd
Heatmap sub-headings in capitals

![Heatmap Depicting Success Across Tasks](../manuscript/heat_map_figure.png "Heatmap depicting success across tasks according to Feature N category and model class. Labels indicate the number of studies and the median number of stimuli is shown in parentheses."){width="892"}

>>>>

![Heatmap Depicting Success Across Tasks](../manuscript/heat_map_figure_R1.png "Heatmap depicting success across tasks according to Feature N category and model class. Labels indicate the number of studies and the median number of stimuli is shown in parentheses."){width="892"}
